An ultra-low noise, high-voltage piezo driver

### 2015-12-19 piezo.tex
Sketch of intro done
* HV stabilization schematic figure

%% ****** Start of file rsitemplate.tex ****** %
%%
%%   This file has been edited from the original source file.
%%	 The original file is part of the revtex4-1 package indicated below.
%%   Version 4.1 of 9 October 2009.
%%
%
% This is a template for producing documents for use with 
% the REVTEX 4.1 document class and the RSI substyle.
% 
% Copy this file to another name and then work on that file.
% That way, you always have this original template file to use.

\documentclass[aip,rsi,reprint,graphicx,draft]{revtex4-1} % for checking your page length
%\\documentclass[aip,rsi,preprint,graphicx]{revtex4-1} % for review purposes

\usepackage{siunitx}

@@

\author{N.C. Pisenti}
\email[]{npisenti@umd.edu}
\author{B.J. Reschovsky}
\author{D.S. Barker}
\author{A. Restelli}
\author{G.K. Campbell}
%\homepage[]{Your web page}
%\thanks{}
%\altaffiliation{}
\affiliation{Joint Quantum Institute, University of Maryland and NIST}

@@

% Body of paper goes here. Use proper sectioning commands. 
% References should be done using the \cite and \label commands
\section{Introduction}
\label{Sec:Introduction}
Introduction, why we care, overview of circuit design elements/features.

\section{Circuit Design}
\label{Sec:Circuit}
Discussion of individual circuit components

>>>>

%% ****** Start of file rsitemplate.tex ****** %
%%
%%   This file has been edited from the original source file.
%%	 The original file is part of the revtex4-1 package indicated below.
%%   Version 4.1 of 9 October 2009.
%%
%
% This is a template for producing documents for use with 
% the REVTEX 4.1 document class and the RSI substyle.
% 
% Copy this file to another name and then work on that file.
% That way, you always have this original template file to use.
\documentclass[aip,rsi,reprint]{revtex4-1} % for checking your page length
%\documentclass[aip,rsi,reprint,graphicx,draft]{revtex4-1} % for checking your page length
%\\documentclass[aip,rsi,preprint,graphicx]{revtex4-1} % for review purposes

\usepackage{siunitx}
\usepackage{amsmath}

\usepackage{graphicx}
%\usepackage{caption}
%\usepackage{subcaption}

%% Work with illustrator *.ai files...
\DeclareGraphicsRule{.ai}{pdf}{.ai}{}

@@

\author{N.C. Pisenti}
\email[]{npisenti@umd.edu}
\author{B.J. Reschovsky}
\author{D.S. Barker}
\author{A. Restelli}
\author{G.K. Campbell}
%\homepage[]{Your web page}
%\thanks{}
%\altaffiliation{}
\affiliation{Joint Quantum Institute, University of Maryland and National Institute of Standards and Technology}

@@

% Body of paper goes here. Use proper sectioning commands. 
% References should be done using the \cite and \label commands
\section{Introduction}
\label{Sec:Introduction}

Many instrumentation applications in the modern laboratory require agile, low-noise voltage sources that can supply hundreds of volts or more.
Such high-voltage amplifiers are useful for micro-positioning applications, driving piezo-actuated mirrors (e.g., in a scanning Fabry-Per{\`o}t cavity) or diffraction gratings (such as in extended-cavity diode lasers).
Precision high voltage sources can also be used to bias low-noise, high-bandwidth photodiodes [details?], Other applications...? biophysics? medical devices?
Often, these applications are operated in a closed feedback loop, where small voltage changes on top of a large DC voltage are necessary to correct for some disturbance to the system.

Traditionally, laboratory electronics capable of supplying high voltages fall under one of two architectural umbrellas: switching converters, and ``linear'' amplifiers.
DC-DC converters are efficient and can work at very high voltages, but suffer from switching noise and limited control bandwidths.
Linear-type devices are typically constructed from a high-voltage operational amplifier (op-amp), powered either from a high voltage linear regulator or more typically from a secondary switching converter.
While the op-amp provides \SI{100}{\decibel} or more of power-supply noise rejection, a high-voltage op-amp require substantially more power than an equivalent switching circuit.
In either case, the output voltage  $V_{\text{out}}$ is typically given by
\begin{align}
  V_{\text{out}} &= G_p(V_{\text{DC}} + V_{\text{mod}})\, \text{,}
\end{align}
where $G_p$ is the piezo amplifier gain (typically {$G_p\approx \num{10} - \num{20}$} or more), $V_{\text{DC}}$ is a DC setpoint, and $V_{\text{mod}}$ is a modulation input used for closed-loop control.

It is often the case, however, that in closed-loop feedback applications we do not need and often do not want the modulation control to have a high gain.
Because the closed loop gain cannot be increased without limit, $G_p V_{\text{mod}} \gg 1$ means the servo gain $G$ must be proportionally smaller to keep the lock stable.
Because noise added by the servo is suppressed by $1/|G|$ in the large gain limit, if $G$ is limited to achieve a stable lock it is no longer as effective at servoing its own noise.

To avoid this problem, we desire a high voltage amplifier which separates the ``setpoint'' gain $G_p$ from the modulation gain, $G_m$. That is,
\begin{align}
  V_{\text{out}} &= G_p V_{\text{DC}} + G_m V_{\text{mod}}\, \text{,}
  \label{Eq:PiezoTransfer}
\end{align}
where now we can make $G_m \approx 1$.

\section{Circuit Design}
\label{Sec:Circuit}

\begin{figure}[ht]
\includegraphics[width=\linewidth]{fig/PiezoCircuit.ai}
%\captionsetup{justification=justified}
\caption{Schematic of the high voltage stabilization.
The voltage HV is generated using a Texas Instruments DRV2700 high voltage driver in flyback configuration (see Fig.~\ref{Fig:DRV2700}).
A fast, very high slew-rate op-amp senses the output voltage across $R_1$ and $R_2$, and servos it by modulating the node at ``HV floating gnd''.
The $V_{\text{DC}}$ gain is set by $\left(1+R_1/R_2\right)$, while the modulation gain is set by $-R_{\text{mod}}/R_{\text{fb}}$.
The capacitor linking the floating ground node to the output allows the op-amp to remove residual switching noise and stabilize the DC output according to the transfer function given in Eq.~(\ref{Eq:PiezoTransfer}). \label{Fig:PiezoCircuit}}
\end{figure}

Discussion of individual circuit components
